---
title: "tumor_tracer"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(dplyr)
```

Inputs & preprocessing

We have 4 files to open in this case. We've already decided which columns we are dropping, and hence we only read select number of columns.

```{r mutant_export input, echo=FALSE}
mutant_export <- fread('CosmicMutantExport.tsv', sep = '\t', header = TRUE, drop = c("Accession Number", "Gene CDS length", "HGNC ID", "Sample name", "ID_sample", "ID_tumour", "Pubmed_PMID", "ID_STUDY"))
```

```{r rest_mut input, echo=FALSE}
res_mut <- fread('CosmicResistanceMutations.tsv', sep = '\t', header = TRUE, drop=c("Sample Name", "Sample ID", "Transcript", "Pubmed Id", "CGP Study"))
```

```{r reamining inputs, echo=FALSE}
coding_muts <- fread('CosmicCodingMuts.vcf', drop=c("ID", "QUAL", "FILTER"))
non_coding_var <- fread("CosmicNonCodingVariants.vcf", drop=c("ID", "QUAL", "FILTER"))
```

Data Exploration

We shall now explore each dataset to see if there exists any meaningful factors.

coding_muts EDA
First we want to see if #CHROM, POS and ID are all unique for each data point. If so then we can drop them (by not reading them).

```{r coding_muts_eda, echo=FALSE}
length(unique(coding_muts$`#CHROM`)) == nrow(coding_muts)
length(unique(coding_muts$POS)) == nrow(coding_muts)
# length(unique(coding_muts$ID)) == nrow(coding_muts)

# see all the unique values for each column
length(unique(coding_muts$`#CHROM`))
length(unique(coding_muts$POS))
length(unique(coding_muts$REF))
length(unique(coding_muts$ALT))
length(unique(coding_muts$INFO))
```

non_coding_var EDA
```{r non_conding_var_eda, echo=FALSE}
length(unique(non_coding_var$`#CHROM`)) == nrow(non_coding_var)
length(unique(non_coding_var$POS)) == nrow(non_coding_var)
# length(unique(non_coding_var$ID)) == nrow(non_coding_var)

# see all the unique values for each column
length(unique(non_coding_var$`#CHROM`))
length(unique(non_coding_var$POS))
length(unique(non_coding_var$REF))
length(unique(non_coding_var$ALT))
length(unique(non_coding_var$INFO))
```

We can see that aside from #CHROM, most of the multi-class features have at least tens of thousands of categories. Hence it will be unwise to use a histogram to plot the data. Hence we shall just focus on plotting histogram for #CHROM for the coding_muts and non_coding_var.

```{r hist_for_#CHROM, echo=FALSE}

```