---
title: "tumor_tracer"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(dplyr)
```

Inputs

We have 4 files to open in this case. 

```{r inputs, echo=FALSE}
coding_muts <- fread('CosmicCodingMuts.vcf')
mutant_export <- read.table('CosmicMutantExport.tsv', sep = '\t', header = TRUE)
non_coding_var <- fread("CosmicNonCodingVariants.vcf")
res_mut <- read.table('CosmicResistanceMutations.tsv', sep = '\t', header = TRUE)
```

Visual inspection of each file
coding_muts: 

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



